Supporting Information for "Imperfect slope measurements drive overestimation in standard cone model of lake depth"

### 2021-08-16 figures/02_depth_model.Rmd
add supp figure showing proxy-proxy fit, closes #30

>>>>

```{r 02_depth_model_fitted_allproxy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}

dt <- readRDS("../data/01_depth_model/depth_grid.rds") %>%
  dplyr::filter(maxdepth == "maxdepth_false_false")

rsq <- round(broom::glance(lm(.pred ~ lake_maxdepth_m, data = dt))$r.squared, 2)

ggplot(data = dt, aes(x = lake_maxdepth_m, y = .pred)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 42, y = 3,
    label = paste0("R^2 == ", rsq),
    parse = TRUE) +
  annotate("label", x = 25, y = 3,
    label = get_formula(
      lm(.pred ~ lake_maxdepth_m, data = dt)),
    size = 4, fill = "white", label.size = NA) +
  ylab("lake_maxdepth_m (predicted)") +
  # geom_abline() +
  scale_x_continuous(expand = c(0, 0), limits = c(1.5, 50)) +
  scale_y_continuous(expand = c(0, 0), limits = c(1.5, NA)) +
  cowplot::theme_cowplot()
```

### 2021-08-16 manuscript/si_template_2019.tex
add supp figure showing proxy-proxy fit, closes #30

            \item \textbf{Figure S9:} Comparison between reported depth and bathymetry depth

@@

\begin{figure}
      \begin{center}\includegraphics[width=0.45\textwidth]{../figures/gg_effort-1}\end{center}
      \caption{Comparison between characteristics of lakes with bathymetry data against lakes with depth from other sources in the LAGOSUS-Depth product. The distance to urban area metric is calculated using data from the 2018 US Census Urban and Rural Classification.}\label{figS8}
\end{figure}

\clearpage
\begin{figure}
      \begin{center}\includegraphics[width=0.85\textwidth]{../figures/01_contrasts-1}\end{center}
      \caption{Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status.}\label{figS9}
\end{figure}

>>>>

            \item \textbf{Figure S9:} Proxy-proxy model fit showing predicted depth versus measured depth

            \item \textbf{Figure S10:} Comparison between reported depth and bathymetry depth

@@

\begin{figure}
      \begin{center}\includegraphics[width=0.45\textwidth]{../figures/gg_effort-1}\end{center}
      \caption{Comparison between characteristics of lakes with bathymetry data against lakes with depth from other sources in the LAGOSUS-Depth product. The distance to urban area metric is calculated using data from the 2018 US Census Urban and Rural Classification.}\label{figS7}
\end{figure}

\clearpage
\begin{figure}
      \begin{center}\includegraphics[width=0.85\textwidth]{../figures/01_contrasts-1}\end{center}
      \caption{Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status.}\label{figS8}
\end{figure}

\clearpage
\begin{figure}
      \begin{center}\includegraphics[width=0.85\textwidth]{../figures/02_depth_model_fitted_allproxy-1}\end{center}
      \caption{Proxy-proxy model fit showing predicted depth versus measured depth.}\label{figS9}
\end{figure}
